4-QTLinterval and plotting

### 2024-02-21 R/Analysis_v0.6_QTL_GxE_and_mash_comparison.Rmd
feat: QTL analysis using phenotypes from new covariance matrices, incorporated into Figure 3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(here)
```

@@

qtldf <- qtldf %>%
  separate(flank_lo, into = c("CHR", "Pos_Mb_lo"), sep = "_", convert = TRUE) %>%
  separate(flank_hi, into = c("flank", "Pos_Mb_hi"), sep = "_", convert = TRUE) %>%
  mutate(Pos_Mb_lo = round(Pos_Mb_lo, digits = 2),
         Pos_Mb_hi = round(Pos_Mb_hi, digits = 2)) %>%
  select(CHR, Pos_Mb_lo, Pos_Mb_hi, lodcolumn, lod, everything()) %>%
  arrange(CHR, Pos_Mb_lo)

qtlplot <- qtldf %>%
  mutate(phe = case_when(lodcolumn == "FL50" ~ "50% flowering",
                              lodcolumn == "dyln_fl50" ~ "Daylength",
                              lodcolumn == "dyln_change_sec" ~ "daylength change (s)",
                              lodcolumn == "CGDD_12C" ~ "GDD, GR to FL",
                              lodcolumn == "crain_gr2fl" ~ "Rainfall, GR to FL")) %>%
  #filter(phe %in% c("Daylength", "GDD, GR to FL")) %>%
  mutate(POS_lo = Pos_Mb_lo * 1000000,
         POS_hi = Pos_Mb_hi * 1000000)

qtlplot$phe <- factor(qtlplot$phe, 
                      levels = c("50% flowering", "Rainfall, GR to FL",
                                 "GDD, GR to FL", "Daylength",
                                          "daylength change (s)",
                                          "Rainfall, 1 day",
                                                  #"Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum"#,
                                                  #"Rainfall, 7d sum"
                                                  ))
```

@@

# Get any mash overlaps for QTL intervals
```{r}
pw_3f <- pw_gf %>%
  full_join(pw_mf) %>%
  full_join(pw_gamf) %>%
  arrange(Chr, Pos) %>%
  filter(log10BayesFactor > 3) %>%
  select(Chr:Pos, log10BayesFactor, subpop, phenotype, everything())

pw_3f_all <- pw_gf %>%
  full_join(pw_mf) %>%
  full_join(pw_gamf) %>%
  arrange(Chr, Pos) %>%
  select(Chr:Pos, log10BayesFactor, subpop, phenotype, everything())

qtlplot
summary(pw_3f$log10BayesFactor)
quantile(pw_gf$log10BayesFactor, 0.96196895)
quantile(pw_gf$log10BayesFactor, 0.96196895)
quantile(pw_gamf$log10BayesFactor, 0.8006157)
1-0.96196895
1-0.8006157
2/464  # GT 0.5%? No 0.0043%
22/418 # GT 3.8031? Yes 5.26%
42/255 # GT 19.93843%? No 16.47%
```

```{r}
i=1  # from 1 to 16
## In block & > 2
QTLandBF <- pw_3f %>%
  filter(Chr %in% qtlplot$CHR[i] & between(Pos, qtlplot$POS_lo[i], qtlplot$POS_hi[i])) %>%
  group_by(subpop) %>% tally()
## BF>2
inBF <- pw_3f %>%
  group_by(subpop) %>% tally()
## BF not > 2 (all minus BF > 2, all is below)
allwrtBF <- pw_3f_all %>%
  group_by(subpop) %>% tally()
## All in block
inQTL <- pw_3f_all %>%
  filter(Chr %in% qtlplot$CHR[i] & between(Pos, qtlplot$POS_lo[i], qtlplot$POS_hi[i])) %>%
  group_by(subpop) %>% tally()

@@

get_QTL_enrichment <- function(m, qtl_df, quantile = 0.95){
  pw_df_all <- get_post_weights(m)

  BFthresh <- quantile(pw_df_all$log10BayesFactor, quantile)
  pw_df <- pw_df_all %>%
  filter(log10BayesFactor > BFthresh) %>%
  select(Chr:Pos, log10BayesFactor, everything())

@@

qtlplot <- qtlplot %>%
  arrange(desc(lod)) %>%
  mutate(pos = as.integer(pos)) %>%
  group_by(CHR, pos) %>%
  slice(1) %>%
  arrange(CHR, pos)
enrich_gf <- get_QTL_enrichment(m_gulf_fl_hyp, qtl_df = qtlplot, 0.99) %>%
  mutate(subpop = "Gulf", phenotype = "flowering")
enrich_mf <- get_QTL_enrichment(m_midw_fl_hyp, qtl_df = qtlplot, 0.99) %>%
  mutate(subpop = "Midwest", phenotype = "flowering")
enrich_gamf <- get_QTL_enrichment(m_gam_fl_hyp, qtl_df = qtlplot, 0.99) %>%
  mutate(subpop = "Both", phenotype = "flowering")

enrich_df <- enrich_gf %>%
  full_join(enrich_mf) %>%
  full_join(enrich_gamf) %>%
  arrange(Chr, Pos_lo)
enrich_df <- enrich_df %>%
  left_join(qtlplot, by = c("Chr" = "CHR", "Pos_lo" = "POS_lo", "Pos_hi" = "POS_hi")) %>%
  select(Chr, Pos_lo, Pos_hi, inQTLandBF:subpop, lod, lodcolumn, pos) %>%
  unique() %>%
  arrange(Chr, Pos_lo, lodcolumn)

@@

t.test(enrich_df[enrich_df$pvalue < 0.05,]$lod, enrich_df[enrich_df$pvalue >= 0.05,]$lod) 
qtlplot %>% group_by(CHR, POS_lo) %>% tally() # 21-24 unique QTL by Pos lo/hi. 23 by QTL maximum. 12 of 24 have enriched mash hits.

@@

for(j in 1:1000){
  qtl_size <- qtlplot %>%
    select(CHR, POS_lo, POS_hi) %>%
    unique() %>%   # don't doublecount completely overlapping QTL
    #(does doublecount partially overlapping QTL, however.)
    group_by(CHR, POS_lo) %>%
    dplyr::mutate(Size = POS_hi - POS_lo) %>%
    dplyr::select(CHR, POS_lo, Size)

@@

  random_gf <- get_QTL_enrichment(m_gulf_fl_hyp, qtl_df = random_qtl, 0.99) %>%
    mutate(subpop = "Gulf", phenotype = "flowering")
  random_mf <- get_QTL_enrichment(m_midw_fl_hyp, qtl_df = random_qtl, 0.99) %>%
    mutate(subpop = "Midwest", phenotype = "flowering")
  random_gamf <- get_QTL_enrichment(m_gam_fl_hyp, qtl_df = random_qtl, 0.99) %>%
    mutate(subpop = "Both", phenotype = "flowering")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(here)
library(data.table)
```

@@

qtldf <- qtldf %>%
  separate(flank_lo, into = c("CHR", "Pos_Mb_lo"), sep = "_", convert = TRUE) %>%
  separate(flank_hi, into = c("flank", "Pos_Mb_hi"), sep = "_", convert = TRUE) %>%
  mutate(Pos_Mb_lo = round(Pos_Mb_lo, digits = 2),
         Pos_Mb_hi = round(Pos_Mb_hi, digits = 2)) %>%
  dplyr::select(CHR, Pos_Mb_lo, Pos_Mb_hi, lodcolumn, lod, everything()) %>%
  arrange(CHR, Pos_Mb_lo)

qtlplot <- qtldf %>%
  mutate(phe = case_when(lodcolumn == "FL50" ~ "flowering",
                              lodcolumn == "dyln_change_sec_2d_prior" ~ "daylength change (s) 2d prior",
                              lodcolumn == "dyln_change_sec" ~ "daylength change (s) 1d prior",
                              lodcolumn == "GR50" ~ "greenup",
                              lodcolumn == "crain_gr2fl" ~ "Rainfall, GR to FL")) %>%
  #filter(phe %in% c("Daylength", "GDD, GR to FL")) %>%
  mutate(POS_lo = Pos_Mb_lo * 1000000,
         POS_hi = Pos_Mb_hi * 1000000)

qtlplot$phe <- factor(qtlplot$phe, 
                      levels = c("flowering", "daylength change (s) 2d prior",
                                 "GDD, GR to FL", "Daylength",
                                          "daylength change (s)",
                                          "Rainfall, 1 day",
                                                  #"Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum"#,
                                                  #"Rainfall, 7d sum"
                                                  ))
```

@@

# Get any mash overlaps for QTL intervals
```{r}
pw_3f <- pw_gf %>%
  filter(log10BayesFactor > 2.56) %>%
  full_join(filter(pw_mf, log10BayesFactor > 2)) %>%
  full_join(filter(pw_gamf, log10BayesFactor > 2.65)) %>%
  arrange(Chr, Pos) %>%
  #filter(log10BayesFactor > 3) %>%
  dplyr::select(Chr:Pos, log10BayesFactor, subpop, phenotype, everything())

pw_3f_all <- pw_gf %>%
  full_join(pw_mf) %>%
  full_join(pw_gamf) %>%
  arrange(Chr, Pos) %>%
  dplyr::select(Chr:Pos, log10BayesFactor, subpop, phenotype, everything())

qtlplot
summary(pw_3f$log10BayesFactor)
quantile(pw_gf$log10BayesFactor, 0.99)  # Gulf: Use 2.56
quantile(pw_mf$log10BayesFactor, 0.99)  # Midwest: Use 2
quantile(pw_gamf$log10BayesFactor, 0.99)  # GAM: Use 2.65
quantile(pw_mf$log10BayesFactor, 0.995119)

quantile(pw_gg$log10BayesFactor, 0.99)  # Gulf: Use 2.0989
quantile(pw_mg$log10BayesFactor, 0.99)  # Midwest: Use 4.6831
quantile(pw_gamg$log10BayesFactor, 0.99)  # GAM: Use 3.0865

1-0.96196895
1-0.8006157
2/464  # GT 0.5%? No 0.0043%
22/418 # GT 3.8031? Yes 5.26%
42/255 # GT 19.93843%? No 16.47%

pw_3g <- pw_gg %>%
  filter(log10BayesFactor > 2.0989) %>%
  full_join(filter(pw_mg, log10BayesFactor > 4.6831)) %>%
  full_join(filter(pw_gamg, log10BayesFactor > 3.0865)) %>%
  arrange(Chr, Pos) %>%
  #filter(log10BayesFactor > 3) %>%
  dplyr::select(Chr:Pos, log10BayesFactor, subpop, phenotype, everything())
```
## SNPs sig in 1% tail or BF>2, whichever is stricter:
```{r}
pw_3f %>%
  arrange(desc(log10BayesFactor)) %>%
  pivot_longer(cols = null:flowering.simple_het_1.13, names_to = "Covar Matrix", values_to = "Posterior Weight") %>%
  filter(`Posterior Weight` > 0.01) %>%
  arrange(desc("Posterior Weight"))

pw_3g %>%
  arrange(desc(log10BayesFactor)) %>%
  pivot_longer(cols = null:greenup.singleton.MO.15, names_to = "Covar Matrix", values_to = "Posterior Weight") %>%
  filter(`Posterior Weight` > 0.01) %>%
  arrange(desc("Posterior Weight"))
```
3,4,6 >99% on gulf.crain_7d

1,2,8 on singleton.TX3 9.3e-01
5 on flowering.si

```{r}
qtlplot_fl <- qtlplot %>% 
  filter(lodcolumn %in% c("FL50", "dyln_change_sec_2d_prior")) 
qtlplot_gr <- qtlplot %>% 
  filter(lodcolumn %in% c("GR50", "dyln_change_sec"))

i=1  # from 1 to 16
## In block & > 2
QTLandBF <- pw_3f %>%
  filter(Chr %in% qtlplot$CHR[i] & between(Pos, qtlplot$POS_lo[i], qtlplot$POS_hi[i])) %>%
  group_by(subpop) %>% tally()
## BF>2
inBF <- pw_3f %>%
  group_by(subpop) %>% tally()
## BF not > 2 (all minus BF > 2, all is below)
allwrtBF <- pw_3f_all %>%
  group_by(subpop) %>% tally()
## All in block
inQTL <- pw_3f_all %>%
  filter(Chr %in% qtlplot$CHR[i] & between(Pos, qtlplot$POS_lo[i], qtlplot$POS_hi[i])) %>%
  group_by(subpop) %>% tally()

@@

get_QTL_enrichment <- function(m, qtl_df, quantile = 0.95){
  pw_df_all <- get_post_weights(m)
  if("lod" %in% colnames(qtl_df)) {
    qtl_df <- qtl_df %>%
      arrange(desc(lod)) %>%
      mutate(pos = as.integer(pos)) %>%
      group_by(CHR, pos) %>%
      dplyr::slice(1) %>%
      arrange(CHR, pos)
  }

  BFthresh <- quantile(pw_df_all$log10BayesFactor, quantile)
  pw_df <- pw_df_all %>%
    filter(log10BayesFactor > BFthresh) %>%
    dplyr::select(Chr:Pos, log10BayesFactor, everything())

@@

enrich_gf <- get_QTL_enrichment(m_gulf_fl_hyp, qtl_df = qtlplot_fl, 0.99) %>%
  mutate(subpop = "Gulf", phenotype = "flowering")
enrich_mf <- get_QTL_enrichment(m_midw_fl_hyp, qtl_df = qtlplot_fl, 0.99) %>%
  mutate(subpop = "Midwest", phenotype = "flowering")
enrich_gamf <- get_QTL_enrichment(m_gam_fl_hyp, qtl_df = qtlplot_fl, 0.99) %>%
  mutate(subpop = "Both", phenotype = "flowering")

enrich_df <- enrich_gf %>%
  full_join(enrich_mf) %>%
  full_join(enrich_gamf) %>%
  arrange(Chr, Pos_lo)
enrich_df <- enrich_df %>%
  left_join(qtlplot_fl, by = c("Chr" = "CHR", "Pos_lo" = "POS_lo", "Pos_hi" = "POS_hi")) %>%
  dplyr::select(Chr, Pos_lo, Pos_hi, inQTLandBF:subpop, lod, lodcolumn, pos) %>%
  unique() %>%
  arrange(Chr, Pos_lo, lodcolumn)

@@

t.test(enrich_df[enrich_df$pvalue < 0.05,]$lod, enrich_df[enrich_df$pvalue >= 0.05,]$lod) 
qtlplot_fl %>% group_by(CHR, POS_lo) %>% tally() # 21-24 unique QTL by Pos lo/hi. 23 by QTL maximum. 12 of 24 have enriched mash hits.

@@

for(j in 1:1000){
  qtl_size <- qtlplot_fl %>%
    dplyr::select(CHR, POS_lo, POS_hi) %>%
    dplyr::distinct() %>%   # don't doublecount completely overlapping QTL
    #(does doublecount partially overlapping QTL, however.)
    group_by(CHR, POS_lo) %>%
    dplyr::mutate(Size = POS_hi - POS_lo) %>%
    dplyr::select(CHR, POS_lo, Size)

@@

  random_gf <- get_QTL_enrichment(m = m_gulf_fl_hyp, qtl_df = random_qtl, 0.99) %>%
    mutate(subpop = "Gulf", phenotype = "flowering")
  random_mf <- get_QTL_enrichment(m_midw_fl_hyp, qtl_df = random_qtl, 0.99) %>%
    mutate(subpop = "Midwest", phenotype = "flowering")
  random_gamf <- get_QTL_enrichment(m_gam_fl_hyp, qtl_df = random_qtl, 0.99) %>%
    mutate(subpop = "Both", phenotype = "flowering")

@@

### Same process for greenup

```{r}

enrich_gg <- get_QTL_enrichment(m_gulf_gr_hyp, qtl_df = qtlplot_gr, 0.95) %>%
  mutate(subpop = "Gulf", phenotype = "greenup")
enrich_mg <- get_QTL_enrichment(m_midw_gr_hyp, qtl_df = qtlplot_gr, 0.9959) %>%
  mutate(subpop = "Midwest", phenotype = "greenup")
enrich_gamg <- get_QTL_enrichment(m_gam_gr_hyp, qtl_df = qtlplot_gr, 0.95) %>%
  mutate(subpop = "Both", phenotype = "greenup")

enrich_gr <- enrich_gg %>%
  full_join(enrich_mg) %>%
  full_join(enrich_gamg) %>%
  arrange(Chr, Pos_lo)
enrich_gr <- enrich_gr %>%
  left_join(qtlplot_gr, by = c("Chr" = "CHR", "Pos_lo" = "POS_lo", "Pos_hi" = "POS_hi")) %>%
  dplyr::select(Chr, Pos_lo, Pos_hi, inQTLandBF:subpop, lod, lodcolumn, pos) %>%
  unique() %>%
  arrange(Chr, Pos_lo, lodcolumn)

enrich_gr %>%
  filter(pvalue < 0.05)

t.test(enrich_gr[enrich_gr$pvalue < 0.05,]$lod, enrich_gr[enrich_gr$pvalue >= 0.05,]$lod) 
qtlplot_gr %>% group_by(CHR, POS_lo) %>% tally() # 21-24 unique QTL by Pos lo/hi. 23 by QTL maximum. 12 of 24 have enriched mash hits.

### 2024-02-21 R/Analysis_v0.6_QTL_interval_plotting.Rmd
feat: QTL analysis using phenotypes from new covariance matrices, incorporated into Figure 3

```{r prep QTL_Eff df}
###QTL Effect plot
###load the original cross and reduce the markers from 4700 to 1185
load('../phenology-fourway/5-QTLmappingForAlice/sexAveraged.cross.rda', verbose = T)
map  =  lapply(pull.map(cross), function(x) x[1,])
# reduced_markers  =  unlist(
#   lapply(
#     reduce_markers(
#       lapply(pull.map(cross), function(x)
#         x[1,]), min_distance = 1), names))
#
# mars2drop  =  markernames(cross)[!markernames(cross) %in% reduced_markers]
# cross  =  drop.markers(cross, mars2drop)
cross = calc.genoprob(cross, step=1, error.prob = 1e-3,map.function = "kosambi",stepwidth = "max")
######### Converting probalibity from qtl1 to qtl2
probs  =  probs_qtl_to_qtl2(cross)$probs
##calculate the kinship matrix for single site
kinship_loco_Single = calc_kinship(probs,use_allele_probs = F,type = "loco")

@@

######get the phenotype at each site
phenology = read.csv('../phenology-fourway/5-QTLmappingForAlice/FL50_phenotypes_Alice.csv', header = TRUE)
colnames(phenology)[1:2] = c('ID','Covariate')
str(phenology) ###make sure your phenology traits are numeric, if not, change them into numeric
phenos <- phenology %>% mutate_at(vars('ID'), list(as.character)) %>%
  mutate_at(vars('ID'), list(as.numeric))%>% group_by(Covariate,ID ) %>%
  summarize_all(mean, na.rm=T) %>% ungroup()%>% as.data.frame()
```

>>>>

```{r prep QTL_Eff df}
###QTL Effect plot
###load the original cross and reduce the markers from 4700 to 1185
#load('../phenology-fourway/5-QTLmappingForAlice/sexAveraged.cross.rda', verbose = T)
load(file.path(workingdir, 'cross_reduced_marker_FL50_phenotypes_Alice_7_SITES.RData'))
map  =  lapply(pull.map(cross), function(x) x[1,])
# reduced_markers  =  unlist(
#   lapply(
#     reduce_markers(
#       lapply(pull.map(cross), function(x)
#         x[1,]), min_distance = 1), names))
#
# mars2drop  =  markernames(cross)[!markernames(cross) %in% reduced_markers]
# cross  =  drop.markers(cross, mars2drop)
cross = calc.genoprob(cross, step=1, error.prob = 1e-3,map.function = "kosambi",stepwidth = "max")
######### Converting probalibity from qtl1 to qtl2
probs  =  probs_qtl_to_qtl2(cross)$probs
##calculate the kinship matrix for single site
kinship_loco_Single = calc_kinship(probs,use_allele_probs = F,type = "loco")

@@

######get the phenotype at each site
phenology = read.csv('../phenology-fourway/5-QTLmappingForAlice/FL50_phenotypes_Alice.csv', header = TRUE)
colnames(phenology)[1:2] = c('ID','Covariate')
str(phenology) ###make sure your phenology traits are numeric, if not, change them into numeric
phenos <- phenology %>% 
  mutate_at(vars('ID'), list(as.character)) %>%
  mutate_at(vars('ID'), list(as.numeric)) %>% 
  group_by(Covariate,ID ) %>%
  summarize_all(mean, na.rm=T) %>% 
  ungroup() %>% 
  as.data.frame()
```

### 2024-02-21 R/Analysis_v0.7_QTL_interval_lod_plot.Rmd
feat: QTL analysis using phenotypes from new covariance matrices, incorporated into Figure 3

```{r}
workingdir <- "~/Github/pvdiv-phenology-gxe/phenology-fourway/5-QTLmappingForAlice/"
load(file.path(workingdir, 'cross_reduced_marker_FL50_phenotypes_Alice_7_SITES.RData'))
load(file.path(workingdir, 'scan1Results_FL50_phenotypes_Alice_7_SITES.RData.RData'))

@@

```{r}
threshold_df <- threshold_full %>% as_tibble(rownames = "Threshold") %>%
  pivot_longer(GR50:dyln_change_sec, names_to = "Phenotype", values_to = "LOD")

s1full %>%
  as_tibble(rownames = "Marker") %>%
  pivot_longer(GR50:dyln_change_sec, names_to = "Phenotype", values_to = "LOD") %>%
  separate(Marker, into = c("Chr", "Pos"), sep = "_", remove = FALSE, convert = TRUE) %>%
  filter(!grepl("loc", Chr)) %>%
  ggplot(aes(x = Pos, y = LOD)) + 
  geom_line(aes(color = Phenotype)) +
  geom_hline(data = threshold_df, aes(yintercept = LOD, color = Phenotype, linetype = Phenotype)) +
  facet_wrap(~Chr, nrow = 1, scales = "free_x") +
  switchgrassGWAS::theme_oeco + 
  scale_color_manual(values = c("#CC0066", "#FFCC00", "#006600", "#6600FF", "grey")) + 
  scale_linetype_manual(values = c(4,5,4,4,4)) +
  theme(legend.position = "top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size = 10, face="bold"),
        strip.text = element_text(size = 10, face="bold"),
        axis.title = element_text(size = 10,face="bold"),
        axis.text.x = element_text(size = 10, angle = 45, hjust = 1, vjust = 1),
        ) + 
  xlab("Position (Mb)") + ylab("LOD score") +
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80))

save_plot(filename = "../manuscript/plots/Figure_4_QTL_by_lod_score.svg", base_height = 3, base_width = 13.5, plot = last_plot())
```

@@

```{r}
test_rug1 <- pw_gf %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug2 <- pw_gamf %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug3 <- pw_mf %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug <- pw_gf %>%
  full_join(pw_gamf) %>%
  full_join(pw_mf) %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
```

```{r}
s1full %>%
  as_tibble(rownames = "Marker") %>%
  pivot_longer(GR50:dyln_change_sec, names_to = "Phenotype", values_to = "LOD") %>%
  separate(Marker, into = c("Chr", "Pos"), sep = "_", remove = FALSE, convert = TRUE) %>%
  filter(!grepl("loc", Chr)) %>%
  ggplot(aes(x = Pos, y = LOD)) + 
  geom_line(aes(color = Phenotype)) +
  geom_rug(data = test_rug2, sides = "t", alpha = 0.1) + 
  geom_rug(data = test_rug1, sides = "b", alpha = 0.2) + 
  geom_rug(data = test_rug3, outside = TRUE, sides = "b", alpha = 0.2) + 
  geom_hline(data = threshold_df, aes(yintercept = LOD, color = Phenotype, linetype = Phenotype)) +
  facet_wrap(~Chr, nrow = 1, scales = "free_x") +
  switchgrassGWAS::theme_oeco + 
  scale_color_manual(values = c("#CC0066", "#FFCC00", "#006600", "#6600FF", "grey")) + 
  scale_linetype_manual(values = c(4,5,4,4,4)) +
  theme(legend.position = "top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size = 10, face="bold"),
        strip.text = element_text(size = 10, face="bold"),
        axis.title = element_text(size = 10,face="bold"),
        axis.text.x = element_text(size = 10, angle = 45, hjust = 1, vjust = 1),
        panel.spacing.x = unit(-0., 'cm')
        ) + 
  xlab("Position (Mb)") + ylab("LOD score") +
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80)) + 
  coord_cartesian(clip = "off")
save_plot(filename = "../manuscript/plots/Figure_4_QTL_by_lod_score_w_rugs.svg", base_height = 3, base_width = 13.5, plot = last_plot())
```

>>>>

```{r}
workingdir <- "~/Github/pvdiv-phenology-gxe/phenology-fourway/5-QTLmappingForAlice/"
load(file.path(workingdir, 'cross_reduced_marker_FL50_phenotypes_Alice_7_SITES.RData'))
load(file.path(workingdir, 'scan1Results_FL50_phenotypes_Alice_7_SITES.RData'))

@@

    flowering_cumulative_rainfall_7d    blue            1
    flowering_daylength_change_s_2d     pink            4  
    flowering                           purple          5

    greenup_daylength_14d               green           2
    greenup_daylength_change_s_1d       yellow          3
    greenup                             grey            6
    greenup_temp_ave_1d                 darkorange      7

```{r}
threshold_df <- threshold_full %>% 
  as_tibble(rownames = "Threshold") %>%
  pivot_longer(GR50:crain_7d, names_to = "Phenotype", values_to = "LOD") %>%
  mutate(Phe = case_when(Phenotype %in% c("GR50", "tave_1d", "dyln_14d_prior", "dyln_change_sec") ~ "greenup",
                         Phenotype %in% c("FL50", "dyln_change_sec_2d_prior", "crain_7d") ~ "flowering", 
                         TRUE ~ NA_character_))

s1full %>%
  as_tibble(rownames = "Marker") %>%
  pivot_longer(GR50:crain_7d, names_to = "Phenotype", values_to = "LOD") %>%
  mutate(Phe = case_when(Phenotype %in% c("GR50", "tave_1d", "dyln_14d_prior", "dyln_change_sec") ~ "greenup",
                         Phenotype %in% c("FL50", "dyln_change_sec_2d_prior", "crain_7d") ~ "flowering", 
                         TRUE ~ NA_character_)) %>% 
  separate(Marker, into = c("Chr", "Pos"), sep = "_", remove = FALSE, convert = TRUE) %>%
  filter(!grepl("loc", Chr)) %>%
  ggplot(aes(x = Pos, y = LOD)) + 
  geom_line(aes(color = Phenotype)) +
  geom_hline(data = threshold_df, aes(yintercept = LOD, color = Phenotype, linetype = Phenotype)) +
  facet_grid(Phe~Chr, scales = "free_x") +
  switchgrassGWAS::theme_oeco + 
  scale_color_manual(values = c("#000099", "#006600", "#FFCC00", "#CC0066", "#6600FF", "grey", "darkorange", "#000666")) + 
  scale_linetype_manual(values = c(4,4,4,4,4,4,4)) +
  theme(legend.position = "top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size = 10, face="bold"),
        strip.text = element_text(size = 10, face="bold"),
        axis.title = element_text(size = 10,face="bold"),
        axis.text.x = element_text(size = 10, angle = 45, hjust = 1, vjust = 1),
        ) + 
  xlab("Position (Mb)") + ylab("LOD score") +
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80))

save_plot(filename = "../manuscript/revision2/Figure_4_QTL_by_lod_score.svg", base_height = 5, base_width = 13.5, plot = last_plot())
```

@@

```{r}
test_rug1 <- pw_gf %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug2 <- pw_gamf %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug3 <- pw_mf %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug <- pw_gf %>%
  full_join(pw_gamf) %>%
  full_join(pw_mf) %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)

test_rug4 <- pw_gg %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug5 <- pw_gamg %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
test_rug6 <- pw_mg %>%
  filter(log10BayesFactor > 2) %>% 
  mutate(Pos = Pos/1000000, 
         LOD = -0.5)
```

```{r}
s1full %>%
  as_tibble(rownames = "Marker") %>%
  pivot_longer(GR50:crain_7d, names_to = "Phenotype", values_to = "LOD") %>%
  filter(Phenotype %in% c("FL50", "dyln_change_sec_2d_prior", "crain_7d")) %>% 
  separate(Marker, into = c("Chr", "Pos"), sep = "_", remove = FALSE, convert = TRUE) %>%
  filter(!grepl("loc", Chr)) %>%
  ggplot(aes(x = Pos, y = LOD)) + 
  geom_line(aes(color = Phenotype)) +
  geom_rug(data = test_rug2, sides = "t", alpha = 0.1) + 
  geom_rug(data = test_rug1, sides = "b", alpha = 0.2) + 
  geom_rug(data = test_rug3, outside = TRUE, sides = "b", alpha = 0.2) + 
  geom_hline(data = filter(threshold_df, 
                           Phenotype %in% c("FL50", "dyln_change_sec_2d_prior", "crain_7d")),
             aes(yintercept = LOD, color = Phenotype, linetype = Phenotype)) +
  facet_wrap(~Chr, nrow = 1, scales = "free_x") +
  switchgrassGWAS::theme_oeco + 
  scale_color_manual(values = c("#000099", "#CC0066", "darkgrey", "#000666")) + 
  scale_linetype_manual(values = c(4,4,4,4,4)) +
  theme(legend.position = "top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size = 10, face="bold"),
        strip.text = element_text(size = 10, face="bold"),
        axis.title = element_text(size = 10,face="bold"),
        axis.text.x = element_text(size = 10, angle = 45, hjust = 1, vjust = 1),
        ) + 
  xlab("Position (Mb)") + ylab("LOD score") +
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80)) + 
  coord_cartesian(clip = "off")
save_plot(filename = "../manuscript/revision2/Figure_4_FL50_QTL_by_lod_score_w_rugs.svg", base_height = 3, base_width = 13.5, plot = last_plot())

s1full %>%
  as_tibble(rownames = "Marker") %>%
  pivot_longer(GR50:crain_7d, names_to = "Phenotype", values_to = "LOD") %>%
  filter(Phenotype %in% c("GR50", "tave_1d", "dyln_14d_prior", "dyln_change_sec")) %>% 
  separate(Marker, into = c("Chr", "Pos"), sep = "_", remove = FALSE, convert = TRUE) %>%
  filter(!grepl("loc", Chr)) %>%
  ggplot(aes(x = Pos, y = LOD)) + 
  geom_line(aes(color = Phenotype)) +
  geom_rug(data = test_rug5, sides = "t", alpha = 0.1) + 
  geom_rug(data = test_rug4, sides = "b", alpha = 0.2) + 
  geom_rug(data = test_rug6, outside = TRUE, sides = "b", alpha = 0.2) + 
  geom_hline(data = filter(threshold_df, 
                           Phenotype %in% c("GR50", "tave_1d", "dyln_14d_prior", 
                                            "dyln_change_sec")), 
             aes(yintercept = LOD, color = Phenotype, linetype = Phenotype)) +
  facet_wrap(~Chr, nrow = 1, scales = "free_x") +
  switchgrassGWAS::theme_oeco + 
  scale_color_manual(values = c("#006600", "#FFCC00",  "grey", "darkorange", "#000666")) + 
  scale_linetype_manual(values = c(4,4,4,4,4,4)) +
  theme(legend.position = "top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text = element_text(size = 10, face="bold"),
        strip.text = element_text(size = 10, face="bold"),
        axis.title = element_text(size = 10,face="bold"),
        axis.text.x = element_text(size = 10, angle = 45, hjust = 1, vjust = 1),
        ) + 
  xlab("Position (Mb)") + ylab("LOD score") +
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80)) + 
  coord_cartesian(clip = "off")
save_plot(filename = "../manuscript/revision2/Figure_4_GR50_QTL_by_lod_score_w_rugs.svg", base_height = 3, base_width = 13.5, plot = last_plot())
```
